cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Added sphere overall paragraph

>>>>

Sphere-shaped structures are useful for evaluating how dimension reduction and clustering algorithms handle curved, symmetric manifolds in high-dimensional spaces. The package provides functions to generate a variety of spherical forms, including simple circles, uniform spheres, grid-based spheres, and complex arrangements like clustered spheres within a larger sphere. These shapes help test how well methods preserve symmetry, curvature, and cluster separation. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:sphere-tb-html)', '\\@ref(tab:sphere-tb-pdf)'))` summarizes these functions.

### 2025-06-24 paper-cardinalR.tex
Added sphere overall paragraph

>>>>

Sphere-shaped structures are useful for evaluating how dimension reduction and clustering algorithms handle curved, symmetric manifolds in high-dimensional spaces. The package provides functions to generate a variety of spherical forms, including simple circles, uniform spheres, grid-based spheres, and complex arrangements like clustered spheres within a larger sphere. These shapes help test how well methods preserve symmetry, curvature, and cluster separation. Table \ref{tab:sphere-tb-pdf} summarizes these functions.
